---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# butcher

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/jyuu/butcher.svg?branch=master)](https://travis-ci.org/jyuu/butcher)
[![Codecov test coverage](https://codecov.io/gh/jyuu/butcher/branch/master/graph/badge.svg)](https://codecov.io/gh/jyuu/butcher?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of butcher is to reduce the size of modeling objects saved to disk. 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jyuu/butcher")
```

## Butchering 

This package provides five S3 generics for you to remove extraneous parts of a model object:

- `axe_call`: To remove the call object.
- `axe_ctrl`: To remove controls associated with training.
- `axe_data`: To remove the original data.
- `axe_env`: To remove inherited environments.
- `axe_fitted`: To remove fitted values.

This is helpful as modeling pipelines might include junk that often gets saved along with a fitted model object. As an example, we take a simple `lm` approach: 

```{r example}
library(butcher)
# basic example
in_house_model <- function() {
  some_junk_in_the_environment <- matrix(1:1e6, ncol = 10) # we didn't know about
  lm(mpg ~ ., data = mtcars) 
}
```

The `lm` that exists in our pipeline is: 

```{r, warning = F, message = F}
library(lobstr)
obj_size(in_house_model())
```

When, in fact, it's a simple `lm` model that should only require: 

```{r, warning = F, message = F}
small_lm <- lm(mpg ~ ., data = mtcars) 
obj_size(small_lm)
```

We don't want to end up saving this new `in_house_model()` on disk, when we could have something like `small_lm` that takes up less memory. So what the heck is going on here? We can examine this with the `butcher` package: 

```{r, warning = F, message = F}
big_lm <- in_house_model()
butcher::weigh(big_lm, threshold = 0, units = "MB")
```

The problem here is in the `terms` component of `big_lm`. Because of how `lm` is implemented in the `stats` package, the environment in which the `lm` model was created was carried along in the model output. To remove this extraneous component, we leverage the `axe_env` generic within `butcher`. In other words, 

```{r, warning = F, message = F}
cleaned_lm <- butcher::axe_env(big_lm)
```

Comparing it against our `small_lm`, we'll find:

```{r, warning = F, message = F}
butcher::weigh(cleaned_lm, threshold = 0, units = "MB")
```

...it now takes the same memory on disk as `small_lm`:

```{r, warning = F, message = F}
butcher::weigh(small_lm, threshold = 0, units = "MB")
```

Axing the environment, however, is not the only functionality of `butcher`. We can also remove `call`, `ctrl`, `data` and `fitted_values`, or simply run `butcher` to execute all of these axing functions at once. Any kind of axing on the object will append a butchered class to the current model object class(es). 

## Model Object Coverage

The current axe methods have been tested on all `parsnip` model objects as listed [here](https://tidymodels.github.io/parsnip/articles/articles/Models.html). If you are working with a new model object that could benefit from any kind of axing, we would love for you to make a pull request. Templates for adding your modeling package and model object to `butcher` are available in this package's `new_model_butcher` function. 
